Resilience and Home-Space for WSTS \thanks{This work was partly done while the authors were supported by the Agence Nationale de la Recherche grant BraVAS (ANR-17-CE40-0028).}

### 2023-10-26 VMCAI-revised-version/final.tex
up

		& VASS & \\\cline{2-3}
		& ~ Reset-VASS, WSTS ($\pred$-basis-effective) Prop~\ref{indec WSTS with dcs}~ 
		& Undecidable   \\ \hline
   \multirow{2}{*}{{\bf BRP }} 
   		 & VASS 
   		 & Decidable   \\\cline{2-3}
~	&  ? & Undecidable    \\ \hline
   \multirow{2}{*}{{\bf kRP }} 
~	& VASS
		& Decidable \\\cline{2-3}
~	& ? & Undecidable    \\ \hline

   \multirow{2}{*}{{\bf sRP }} 
   		 & WSTS (downward + upward) Thm~9 & Decidable\\ \cline{2-3}
~	& ~ Reset-VASS, WSTS ($\pred$-basis-effective) Prop~\ref{srp up down} ~ & Undecidable  \\ \hline
   \multirow{2}{*}{{\bf BsRP }} 
   		 & WSTS (downward + upward) Cor~\ref{downward brp} & Decidable \\ \cline{2-3}
~	&  ? & Undecidable   \\ \hline
   \multirow{2}{*}{{\bf ksRP }} 
   		 & WSTS (downward + upward) Cor~\ref{downward brp} & Decidable\\ \cline{2-3}
~	 & ? & Undecidable    \\ \hline

>>>>

		& VASS & \\\cline{2-3}
		& ~ Reset-VASS, WSTS ($\pred$-basis-effective) Prop~\ref{indec WSTS with dcs} 
		& Undecidable   \\ \hline
   \multirow{2}{*}{{\bf BRP }} 
   		 & VASS 
   		 & Decidable   \\\cline{2-3}
~	&  ? & Undecidable    \\ \hline
   \multirow{2}{*}{{\bf kRP }} 
~	& VASS
		& Decidable \\\cline{2-3}
~	& ? & Undecidable    \\ \hline

   \multirow{2}{*}{{\bf sRP ~ ~ }} 
   		 & WSTS (downward + upward) Thm~9 & Decidable\\ \cline{2-3}
~	& ~ Reset-VASS, WSTS ($\pred$-basis-effective) Prop~\ref{srp up down}  & Undecidable  \\ \hline
   \multirow{2}{*}{{\bf BsRP }} 
   		 & WSTS (downward + upward) Cor~\ref{downward brp} & Decidable \\ \cline{2-3}
~	&  ? & Undecidable   \\ \hline
   \multirow{2}{*}{{\bf ksRP }} 
   		 & WSTS (downward + upward) Cor~\ref{downward brp} & Decidable\\ \cline{2-3}
~	 & ? & Undecidable    \\ \hline
